---
output:
  html_document: default
  pdf_document: default
---
```{r setup, include=FALSE}
library(ggplot2)
library(ggdist)
library(gganimate)
library(dplyr)

knitr::opts_chunk$set(echo = TRUE)
```

In this documents, we show how we generate the weather forecast example data and how the visualization stimuli is generated.

## Data generating Process

We generate the data from a Gaussian distribution with a fixed mean and varying variance drawn from a uniform distribution. 

```{r datagenerate}

# Configuration of data generating model
# Daily low temperature follows a Gaussian distribution with a fixed mu and sigma drawn uniformly from {2, 3, 4, 5}
mu = 5
sigma_choices = c(2, 3, 4, 5)
sigma = sample(sigma_choices, 1)

# Size of sample
n_size = 100

low_temp = data.frame(temp = rnorm(n_size, mu, sigma), x=factor(0))
dense_temp = density(low_temp$temp)
```

## Stimuli

We generate four types of stimuli (mean, mean + CI, mean + gradience, and mean + HOPs).

```{r stimuli1}

theme_set(theme_ggdist())
options(repr.plot.width = 10, repr.plot.height =2)

ggplot(data = low_temp, mapping = aes(x=0)) +
  geom_hline(aes(yintercept=mean(temp)),
             size=2, color="red") +
  labs(x = "", y = "") + 
  ylim(-20, 60) + theme(aspect.ratio=4) + 
  theme(panel.background = element_rect(fill = "white", colour = "grey50"))
```

```{r stimuli2}
ggplot(data = low_temp, mapping = aes(x=factor(0)), colour=x) +
  geom_hline(aes(yintercept=mean(temp)),
             size=2, color="red")+
  geom_errorbar(aes(ymin = mean(temp) - sd(temp), ymax = mean(temp) + sd(temp)), 
                width = 0.2) +
  labs(x = "", y = "") +
  theme(axis.text.x = element_blank(),
    axis.ticks = element_blank()) + 
  ylim(-20, 60) + theme(aspect.ratio=4) + 
  theme(panel.background = element_rect(fill = "white", colour = "grey50"))
```

```{r stimuli3}
ggplot() +
  geom_raster(aes(x = 0, y = dense_temp$x, fill = dense_temp$y)) + 
  guides(fill=guide_legend(title="Density")) +
  scale_fill_gradient(low = "white", high = "#7F9FCE") + 
  geom_hline(yintercept=mean(low_temp$temp),
             size=2, color="red") +
  labs(x = "", y = "") +
  theme(axis.text.x = element_blank(),
        axis.ticks = element_blank()) + 
  ylim(-20, 60) + theme(aspect.ratio=4) + theme(legend.position = "none") + 
  theme(panel.background = element_rect(fill = "white", colour = "grey50"))
```

```{r stimuli4}
n_hop_sample = 50

hops_low_temp = low_temp %>% 
  sample_n(n_hop_sample) %>% 
  mutate(sample_id = 1:n_hop_sample) %>% 
  select(hops_temp = temp, everything())

p = hops_low_temp %>% 
  ggplot() +
    geom_hline(yintercept = mean(low_temp$temp),
               size=2, color="red") +
    geom_point(aes(x = 0, y = hops_temp), shape = '-', size=10, color = '#7F9FCE') +
    labs(x = "", y = "") + 
    theme(axis.text.x = element_blank(),
          axis.ticks = element_blank()) + 
    ylim(-20, 60) +
    transition_manual(sample_id) + theme(aspect.ratio=4) + 
    theme(panel.background = element_rect(fill = "white", colour = "grey50"))

p
```


## Scoring rule and expected score

### The setting of scoring rule

We design the scoring rule by action and whether it's freezing. We give no salt but freezing a large penalty ($-100$) while salt but not freezing a smaller one (-10). We hold a zero payoff (no penalty) for no salt without freezing and salt with freezing.

```{r payoff}
# the scoring rule
no_salt_not_freezing_payoff = 0
no_salt_freezing_payoff = -100
salt_not_freezing_payoff = -10
salt_freezing_payoff = 0
```

### Rational baseline and benchmark

- Baseline (rational agent with prior knowledge)

```{r}
# The rational agent's prior belief is the expected possibility of freezing without knowledge about which sigma is
prior_belief = Reduce("+", sapply(sigma_choices, function(m) {pnorm(0, mu, m)})) / 4

# The payoff of salt or no salt
payoff_salt = salt_freezing_payoff * prior_belief + salt_not_freezing_payoff * (1 - prior_belief)
payoff_no_salt = no_salt_freezing_payoff * prior_belief + no_salt_not_freezing_payoff * (1 - prior_belief)

# rational agent's best action and payoff
rprior_action = ifelse(payoff_no_salt > payoff_salt, "No salt", "Salt")
rprior = max(payoff_no_salt, payoff_salt)

rprior
```

- Benchmark (rational agent with visualization)

```{r}
# The rational agent's posterior believes vary from visualization condictions, where we assume that CI, gradient, and HOPs give full information about the distribution and only mean gives no information about sigma.
full_information_belief = sapply(sigma_choices, function(m) {pnorm(0, mu, m)})
only_mean_belief = Reduce("+", sapply(sigma_choices, function(m) {pnorm(0, mu, m)})) / 4

# The payoff of full information
full_information_payoff_salt = sapply(full_information_belief, function(belief) {
  salt_freezing_payoff * belief + salt_not_freezing_payoff * (1 - belief)
})
full_information_payoff_no_salt = sapply(full_information_belief, function(belief) {
  no_salt_freezing_payoff * belief + no_salt_not_freezing_payoff * (1 - belief)
})

# The payoff of only mean
only_mean_payoff_salt = salt_freezing_payoff * only_mean_belief +
  salt_not_freezing_payoff * (1 - only_mean_belief)
only_mean_payoff_no_salt = no_salt_freezing_payoff * only_mean_belief +
  no_salt_not_freezing_payoff * (1 - only_mean_belief)

# rational agent's best actions and payoffs
full_information_actions = ifelse(full_information_payoff_salt > full_information_payoff_no_salt,
                                  "Salt",
                                  "No salt")
only_mean_action = ifelse(only_mean_payoff_salt > only_mean_payoff_no_salt, "Salt", "No salt")

rpos_full_information = Reduce("+", sapply(1:length(full_information_payoff_salt),
                                 function(i) {
                                   max(full_information_payoff_salt[i], full_information_payoff_no_salt[i])
                                 })) / 4

rpos_only_mean = max(only_mean_payoff_salt, only_mean_payoff_no_salt)

list(full_information = rpos_full_information, only_mean = rpos_only_mean)
```

We then draw the expected score of the agent for both no-salt and salt actions as a function of his belief p, where the upper segments represent the rational agent with posterior information's payoff and the lower parts are the theoretical lowerbound of decision's payoff.

```{r}
# The line of no salt
df_no_salt = data.frame(x = c(0, 1), y = c(no_salt_not_freezing_payoff, no_salt_freezing_payoff))
# The line of salt
df_salt = data.frame(x = c(0, 1), y = c(salt_not_freezing_payoff, salt_freezing_payoff))

theme_set(theme_ggdist())
ggplot() +
  geom_line(data = df_no_salt, aes(x, y), color = "#d95f02", size=1) +
  geom_line(data = df_salt, aes(x, y), color = "#7570b3", size=1) +
  geom_point(data = df_no_salt, aes(x, y), color = "#d95f02") +
  geom_point(data = df_salt, aes(x, y), color = "#7570b3") +
  geom_vline(xintercept = 0, linetype="dashed") +
  geom_vline(xintercept = 1, linetype="dashed") +
  theme(aspect.ratio = 0.5) +
  labs(x="Possibility of freezing", y="Payoff")
```
